---
title: "Monday work-week briefing"
subtitle: "Marquette, Michigan"
format: html
---

```{r}
#| include: false
source("R/constants.R")
source("R/nws.R")
source("R/climate.R")
source("R/tasks.R")

library(dplyr)
library(lubridate)

nws_context <- wmw_nws_context()
current <- wmw_nws_current_summary(nws_context)
work_week <- wmw_nws_work_week(nws_context)
rolling <- wmw_rolling_year_series()
tasks <- wmw_monday_tasks(work_week = work_week, current = current, rolling = rolling)
task_table <- wmw_tasks_dataframe(tasks)

briefing_monday <- floor_date(with_tz(Sys.time(), "America/Detroit"), unit = "week", week_start = 1)
briefing_friday <- briefing_monday + days(4)
```

## Week of `r format(briefing_monday, "%B %d")`–`r format(briefing_friday, "%d, %Y")`

Wooden Man Weather publishes a practical outlook each Monday for the Marquette work week. Forecasts come from the National Weather Service; climate context uses NOAA daily summaries for station `r wmw_station_id()`.

**Headline:** `r if (nrow(work_week) > 0) work_week$short_forecast[1] else current$description`

**Observation:** `r wmw_format_f(current$temperature_f)` at `r current$station` (`r wmw_format_dt(current$observed_at)`).

## Work-week strip

```{r}
if (nrow(work_week) == 0) {
  cat("The NWS work-week periods are not available yet. Check the dashboard for the latest forecast.")
} else {
  knitr::kable(
    work_week |>
      transmute(
        Day = name,
        `High (°F)` = ifelse(is_daytime, temperature, NA_real_),
        Forecast = short_forecast,
        `Precip %` = probability_of_precipitation,
        Wind = paste(wind_direction, wind_speed)
      ),
    align = "lcccc"
  )
}
```

## Wooden Man tasks

```{r}
knitr::kable(task_table, col.names = c("Task", "Guidance"), align = "ll")
```

## Data notes

- Normals: `r wmw_normals_start_year()`–`r wmw_normals_end_year()` monthly averages for `r wmw_station_id()`.
- Airport readings may differ from lakeshore or hilltop conditions.
- This page is generated from rule-based seasonal triggers plus the current NWS forecast; edit `R/tasks.R` as the library grows.

[Return to the dashboard](index.qmd)
