---
title: "Weekly outdoor outlook"
subtitle: "Marquette, Michigan"
format: html
---

```{r}
#| include: false
source("R/constants.R")
source("R/nws.R")
source("R/climate.R")
source("R/tasks.R")

library(dplyr)
library(lubridate)

nws_context <- wmw_nws_context()
current <- wmw_nws_current_summary(nws_context)
forecast_7d <- wmw_nws_next_days(nws_context, days = 7)
rolling <- wmw_rolling_year_series()
tasks <- wmw_monday_tasks(work_week = forecast_7d, current = current, rolling = rolling)
task_table <- wmw_tasks_dataframe(tasks)

outlook_start <- as.Date(with_tz(Sys.time(), "America/Detroit"))
outlook_end <- outlook_start + days(6)
```

## `r format(outlook_start, "%B %d")`–`r format(outlook_end, "%d, %Y")`

Wooden Man Weather publishes a practical outdoor outlook for the next seven days in Marquette. Forecasts come from the National Weather Service; climate context uses NOAA daily summaries for station `r wmw_station_id()`. Fair days lean toward Presque Isle, the Fit Strip, and slow hangs outside; foul days lean toward Peter White Library, Dead River Coffee, MarqTran, and a new restaurant.

`r if (nrow(forecast_7d) > 0) forecast_7d$short_forecast[1] else current$description`

`r wmw_format_f(current$temperature_f)` at `r current$station` (`r wmw_format_dt(current$observed_at)`).

## Forecast for next 7 days:

```{r}
if (nrow(forecast_7d) == 0) {
  cat("The NWS 7-day periods are not available yet. Check the dashboard for the latest forecast.")
} else {
  knitr::kable(
    forecast_7d |>
      transmute(
        Day = name,
        `Temp (°F)` = temperature,
        Forecast = short_forecast,
        `Precip %` = probability_of_precipitation,
        Wind = paste(wind_direction, wind_speed)
      ),
    align = "lcccc"
  )
}
```

## Wooden Man tasks

Outdoor first, tied to **this** 7-day forecast. Foul stretches get an indoor backup. No traffic tips — this is Marquette.

```{r}
knitr::kable(task_table, col.names = c("Task", "Guidance"), align = "ll")
```

## Data notes

- Normals: `r wmw_normals_start_year()`–`r wmw_normals_end_year()` monthly averages for `r wmw_station_id()`.
- Airport readings may differ from lakeshore or hilltop conditions.
- **Monday edits:** open `R/tasks.R` and change only the `wmw_manual_monday_tasks` list at the top (hand-written tasks appear first). Leave it as `list()` to use the auto weather/season tasks. Then run `quarto render monday.qmd` or push to `main` and let Actions rebuild.
- Auto rules (warmest/wettest/windiest day, week pattern, winter buck-up) live in the same file below the Monday hook.

[Return to the dashboard](index.qmd)
